# Course Project 1 Reproducible Research

### Code for reading in the dataset and/or processing the data
```{r}
tabla<-read.csv("./activity.csv",header=TRUE)
names(tabla)
str(tabla)
#Tabla que no tiene datos faltantes
tabla1<-tabla[complete.cases(tabla),]
```

### Histogram of the total number of steps taken each day
```{r}
library(ggplot2)
totalpasos<- aggregate(steps ~ date, tabla1, sum)
ggplot(totalpasos,aes(x=steps))+geom_histogram(bins=5,fill="pink",color="red")
```

### Mean and median number of steps taken each day
```{r}
summary(totalpasos$steps)
```


### Time series plot of the average number of steps taken

```{r}
avg_steps_interval<-aggregate(steps~interval,tabla1,mean)
avg_steps_day<-aggregate(steps~date,tabla1,mean)
plot(avg_steps_interval$interval, avg_steps_interval$steps, type='l', col=1, main="Número promedio de pasos por intervalo", xlab="Intervalos de tiempo", ylab="Número promedio de pasos")
```

### The 5-minute interval that, on average, contains the maximum number of steps
```{r}
Intervalo<-which.max(avg_steps_interval$steps)
Pasos<-avg_steps_interval[Intervalo,]$steps
```
El intervalo de 5 minutos que contiene el máximo número de pasos es `r Intervalo` con `r Pasos`.

### Code to describe and show a strategy for imputing missing data
```{r}
#se buscan cuantos datos faltantes hay
datos_faltantes<-tabla[!complete.cases(tabla),]
nrow(datos_faltantes)
#Se ingresan valores promedio en los datos faltantes
for (i in 1:nrow(tabla)) {
    if(is.na(tabla$steps[i])) {
        val <- avg_steps_interval$steps[which(avg_steps_interval$interval == tabla$interval[i])]
        tabla$steps[i] <- val 
    }
}
steps_day_impute <- aggregate(steps ~ date, tabla, sum)
str(steps_day_impute)
```

### Histogram of the total number of steps taken each day after missing values are imputed
```{r}
ggplot(steps_day_impute,aes(x=steps))+geom_histogram(bins=5,fill="white",color="blue")+ggtitle("Histograma con datos imputados")
```

### Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
#Validamos si es un día laboral o de trabajo
week_day <- function(date_val) {
    wd <- weekdays(as.Date(date_val, '%Y-%m-%d'))
    if  (!(wd == 'sábado' || wd == 'domingo')) {
        x <- 'Weekday'
    } else {
        x <- 'Weekend'
    }
    x
}
#Se grafica por tipo de día
tabla$day_type <- as.factor(sapply(tabla$date, week_day))
#Se revisa a qué tipo de día pertenece
steps_day_impute <- aggregate(steps ~ interval+day_type, tabla, mean)
plt <- ggplot(steps_day_impute, aes(interval, steps)) +
        geom_line(stat = "identity", aes(colour = day_type)) +
        facet_grid(day_type ~ ., scales="fixed", space="fixed") +
        labs(x="Intervalo", y=expression("Número de pasos")) +
        ggtitle("Número de pasos por intervalo por tipo de día")
print(plt)
```

All of the R code needed to reproduce the results (numbers, plots, etc.) in the report